Split-Apply-Combine with Dynamic Grouping

### 2023-01-03 paper/article.Rnw
Writing in progress

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Specifying tests}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Specifying tests}
The \code{test} parameter of \code{cumulate()} and \code{accumulate} accepts a
function that takes a subset of the data and must returns a boolean. In
principle this gives users enough flexibility to specify any possible test to
determine whether a collapsing step is necessary or not. However, the package
exports a few utility functions that make common test conditions easier to
express without the need for writing a function. Moreover, to support users
that are not comfortable with function writing, there is a higher order
function called \code{demand()} that makes expressing combinations of
tests easier.

Common test conditions include demanding a minimal number of records, or a
minimal number or fraction of complete records. These cases can be expressed
with helper functions.
%
\begin{center}
\begin{tabular}{ll}
\code{min_records(n,vars)}   & At least $n$ records for variables \code{vars}\\
\code{min_complete(n,vars)}   & At least $n$ records complete records for variables \code{vars}\\
\code{frac_complete(r,vars)} & At least $100r$\% complete records for variables \code{vars}\\
\end{tabular}
\end{center}
